Theories of deliberated choice

### 2023-11-10 simple.tex
Some cleanup

\begin{example}[Big disjunct, not falsifiable]
  \label{ex:bigor}
  $[\forall i: (\ar) \ileadstog \phi] \lor [\forall i: (\ar, \ar) \ileadstog \phi] \lor …$ is not falsifiable.
  Here, $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$.

  Given any $θ$, define $l = \max_{\hist \suchthat \exists p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise. Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}[Disjunct with incompatible paths, not falsifiable]
  \label{ex:disj}
  Given $\ar \neq \ar' \in \allargs$, the claim appearing in \cref{ex:disjR}, namely,
  $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$, is not falsifiable.
  Consider any ${\allleadstog} \notin C$, thus satisfying, for some $i$, $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
  Consider any $θ \subseteq {\allleadstog}$ and let us prove that $\theta \in C^\wsub$.
  By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$. We have ${\allleadstog'} \in \theta \in C^\wsub$.
\end{example}
\begin{example}[Partly falsifiable is still unfalsifiable]
  \label{ex:partlyU}
  Given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
  $\hist \ileadstog[j] \phi \land \forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
  Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
  \Cref{ex:disj} concludes.
\end{example}
\begin{example}
  \label{ex:allParticular}
  Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
  Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}
\begin{example}
  \label{ex:existsParticular}
  Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
  Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $\theta \in C^\wsub$.
\end{example}

@@

>>>>

\begin{example}[Big disjunct, strongly unfalsifiable]
  \label{ex:bigor}
  Consider $\ar \in \allargs$.
  The claim $[\forall i: (\ar) \ileadstog \phi] \lor [\forall i: (\ar, \ar) \ileadstog \phi] \lor …$,
  thus, $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall i: (a)^n \ileadstog \phi}$,
  is strongly unfalsifiable.

  Given any $θ \in \Theta$, define $l = \max_{\hist \suchthat \exists i \in I, p \in P \suchthat (i, \hist, p) \in θ} \card{\hist} + 1$ if $\exists p \in P \suchthat (i, \hist, p) \in θ$, and $l = 1$ otherwise. Pick any $\allleadstog$ such that $θ \subset {\allleadstog} \land (\ar)^l \ileadstog \phi$. We have
  % ${\allleadstog} \in S_θ \cap C ≠ \emptyset$.
  $\theta \in \powerset{\allleadstog}$ and ${\allleadstog} \in C$, thus, $\theta \in C^\wsub$.
\end{example}
\begin{example}[Disjunct with incompatible paths, not falsifiable]
  \label{ex:disj}
  Given $\ar \neq \ar' \in \allargs$, the claim appearing in \cref{ex:disjR}, namely,
  $\forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$, is not falsifiable.
  Consider any ${\allleadstog} \notin C$, thus satisfying, for some $i$, $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$.
  Consider any $θ \subseteq {\allleadstog}$ and let us prove that $\theta \in C^\wsub$.
  By definition of a general observation, $θ$ may not contain both $((\ar), i, \phi)$ and $((\ar'), i, \phi)$, thus letting $t$ denote one of these triples not in $θ$, pick any ${\allleadstog'}$ such that $θ \subset {\allleadstog'} \land t \in {\allleadstog'}$. We have ${\allleadstog'} \in S_θ \cap C ≠ \emptyset$.
\end{example}
\begin{example}[Partly falsifiable is still unfalsifiable]
  \label{ex:partlyU}
  Given $j \in I$, $\hist \in \allhists$ and $\ar \neq \ar' \in \allargs$,
  $\hist \ileadstog[j] \phi \land \forall i: [(\ar) \ileadstog \phi \lor (\ar') \ileadstog \phi]$ is not falsifiable.
  Consider any $\allleadstog$ satisfying $(\ar) \nileadstog \phi \land (\ar') \nileadstog \phi$, thus with ${\allleadstog} \notin C$.
  \Cref{ex:disj} concludes.
\end{example}
\begin{example}
  \label{ex:allParticular}
  Consider any $\ar$ and $\phi$. The claim $\forall i: \ar \ileadstostg \phi$ is falsifiable.
  Given any ${\allleadstog} \notin C$, consider any $i \suchthat \ar \nileadstostg \phi$ and any $\hist \suchthat \hist \nileadstog \phi \land \ar \in \histend$, and define $θ = \set{(i, \hist, {\allleadstog}(i, \hist) ≠ \phi)}$.
\end{example}
\begin{example}
  \label{ex:existsParticular}
  Given an infinite $I$, the claim $\exists i \suchthat \ar \ileadstostg \phi$ is not falsifiable.
  Given any ${\allleadstog} \notin C$, thus such that $\forall i: \ar \nileadstostg \phi$, any $θ \subseteq {\allleadstog}$ only has finitely many $(i, \hist, p ≠ \phi)$ thus $\theta \in C^\wsub$.
\end{example}

@@

\begin{example}[Bigger disjunct, strongly unfalsifiable]
  \label{ex:biggeror}
  Pick any $i \in I$ and $\ar \in \allargs$.
  The claim $[(\ar) \ileadstog \phi] \lor [(\ar, \ar) \ileadstog \phi] \lor …$,
  thus, $C = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat (a)^n \ileadstog \phi}$,
  is strongly unfalsifiable.

  Let $C' = \set{{\allleadstog} \suchthat \exists n \in \N^* \suchthat \forall j: (a)^n \ileadstog[j] \phi}$ denote the claim of \cref{ex:bigor}.
  We have $C' \subseteq C$.
  It follows that ${C'}^\wsub \subseteq C^\wsub$.
  We know from \cref{ex:bigor} that $\Theta \wsub {C'}^\wsub$, thus, $\Theta \wsub C^\wsub$.
\end{example}
